Optimal Task Phasing for End-To-End Latency in Harmonic Systems and Semi-Harmonic Automotive Systems

### 2024-10-07 paper.tex
Added plot with average latency under synchronous release, optimal phasing, random phasing and worst-case latency.
Updated plots and added plot to evaluate number of combinations to check with heuristic

\begin{figure}
	\includegraphics[width=\columnwidth]{plots/LatencyComp.pdf}
	\caption{Comparison of latency under worst-case phasing, synchronous release and optimal phasing. Normalized to the hyperperiod of the chain.}
	\label{fig:latencyComp}
\end{figure}

@@

>>>>

\begin{figure}
	\includegraphics[width=\columnwidth]{plots/AvrgLatencyComp.pdf}
	\caption{Comparison of average latency under worst-case phasing, synchronous release, optimal phasing and random phasing. Normalized to the hyperperiod of the chain.}
	\label{fig:latencyComp}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{plots/HeuristicCombinations.pdf}
	\caption{Phase combinations to check by the heuristic of~\cite{Martinez:LET2018} when phases can be assigned to all but the first tasks.}
	\label{fig:heuristicComp}
\end{figure}
